xolotl: An Intuitive and Approachable Neuron \& Network Simulator

### 2018-08-15 paper/paper.tex
minor changes

\section*{Acknowledgments}
The authors would like to thank Timothy O'Leary and Leandro Alonso for useful discussions, and Janis Li for help transcribing many conductance models.

>>>>

\section*{Acknowledgments}
The authors would like to thank Timothy O'Leary and Leandro Alonso for useful discussions, Janis Li for help transcribing many conductance models, and members of the Marder Lab, especially Ekaterina Morozova, Jason Pipkin and Philipp Rosenbaum for careful reading of the manuscript.
